Handbook streamFind: Backend

### 2023-03-08 README.Rmd

The R package [streamFind](https://github.com/ricardobachertdacunha/streamFind) (this repository) is the back-end framework for the streamFind project entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle". The streamFind project is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of streamFind is data processing for environmental and quality studies. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

@@

@@

For installation of the [streamFind](https://github.com/ricardobachertdacunha/streamFind) R package, it is recommended to firstly ensure that the dependencies are currently installed. Several existing R packages and external software are used in streamFind for various processing steps. A major dependency of streamFind is the [patRoon](https://github.com/rickhelmus/patRoon) R package. The [patRoon](https://github.com/rickhelmus/patRoon) R package combines several tools for basic and advanced data processing and can be used interchangeably with streamFind.

### Install dependencies

[R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only recommended for Windows users). The [handbook](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites) of the [patRoon](https://github.com/rickhelmus/patRoon) R package offers detailed installation instructions, including the required [dependencies](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#other-dependencies).

### Install streamFind

The [streamFind](https://github.com/ricardobachertdacunha/streamFind) R package can be installed from the GitHub repository.

@@

>>>>

The streamFind project, entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle", is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of streamFind is the development and assembly of workflows for processing data from mass spectrometry and spectroscopy and for application the workflows in environmental and quality studies of the water cycle. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

@@

# streamFind R package

The R package [streamFind](https://github.com/ricardobachertdacunha/streamFind) is the back-end framework for the streamFind project and can be obtained with this repository.

@@

For installation of the streamFind R package, it is recommended to first install the dependencies. Besides [R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only recommended for Windows users), the streamFind depends on the [patRoon](https://github.com/rickhelmus/patRoon) R package. The patRoon R package combines several tools for basic and advanced data processing and can be used interchangeably with streamFind. The [handbook](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites) of the patRoon R package offers detailed installation instructions, including the list of required [dependencies](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#other-dependencies).

The streamFind R package can then be installed from the GitHub repository.

@@

### Documentation

The documentation and usage examples of the streamFind package can be found in the [reference page](https://ricardobachertdacunha.github.io/streamFind/reference/index.html) and [articles](https://ricardobachertdacunha.github.io/streamFind/articles/index.html) of the [webpage](https://ricardobachertdacunha.github.io/streamFind/index.html), respectively.
